Computational methods in landscape ecology

### 2024-10-18 Sections/09-conclusion.qmd
Fix table

<!-- MH: Check connectivity, simulations sections again for 'hidden' software -->

| Topic | Programming language | Software | Reference |
|:---:|:---:|:---:|:---:|
| Spatial patterns | R | sf | [@Pebesma2018SimpleFeatures] |
| Spatial patterns | R | terra | [@Hijmans2024TerraSpatial] |
| Spatial patterns | R | landscapemetrics | [@Hesselbarth2019LandscapemetricsOpensource] |
| Spatial patterns | R | multilandr | [@Huais2024MultilandrPackage] |
| Spatial patterns | R | bespatial | [@Nowosad2024BespatialBoltzmann] |
| Spatial patterns | R | rasterdiv | [@Rocchini2021RasterdivInformation] |
| Spatial patterns | R | LandComp | [@Konrad2023AdaptingMultiscale] |
| Spatial patterns | R | geodiv | [@Smith2021GeodivPackage] |
| Spatial patterns | R | glcm | [@Zvoleff2020GlcmCalculate] |
| Spatial patterns | R | GraySpatCon | [@Riitters2023MappingLandscape] |
| Spatial patterns | R | vectormetrics | [@Matuszek2024VectormetricsLandscape] |
| Spatial patterns | R | motif | [@Nowosad2021MotifOpensource] |
| Spatial patterns | Python | GeoPandas | [@Jordahl2020GeopandasPython] |
| Spatial patterns | Python | rasterio | [@Gillies2013RasterioGeospatial] |
| Spatial patterns | Python | PyLandStats | [@Bosch2019PyLandStatsOpensource] |
| Spatial patterns | Julia | GeoStats | [@Hoffimann2018GeoStatsjlHighperformance] |
| Spatial patterns | Julia | GeoInterface | [@JuliaGeoandcontributors2024GeoInterfaceJulia] |
| Spatial patterns | Stand-alone software | FRAGSTATS | [@McGarigal2023FRAGSTATSV4] |
| Spatial patterns | Stand-alone software | GuidosToolbox | [@Vogt2017GuidosToolboxUniversal] |
| Connectivity | R | ResistanceGA | [@Peterman2018ResistanceGAPackage] |
| Connectivity | R | lconnect | [@Mestre2023LconnectPackage] |
| Connectivity | R | grainscape | [@Chubaty2020ToolboxGrainscape] |
| Connectivity | Julia | Circuitscape | [@Anantharaman2019CircuitscapeJulia] |
| Connectivity | Julia | ConScape | [@vanMoorter2023AcceleratingAdvances] |
| Connectivity | Julia | Omniscape | [@Landau2021OmniscapejlSoftware] |
| Connectivity | Stand-alone software | Graphab | [@Foltete2012SoftwareTool] |
| Connectivity | Stand-alone software | Conefor | [@Saura2009ConeforSensinode] |
| Connectivity | Stand-alone software | lscorridors | [@Ribeiro2017LandScapeCorridors] |
| Sampling | Python | ZonalMetrics | [@Adamczyk2017ZonalMetricsPython] |
| Simulations | R | NLMR | [@Sciaini2018NLMRLandscapetools] |
| Simulations | Python | NLMpy | [@Etherington2015NLMpyPython] |
| Simulations | Julia | NeutralLandscapes | [@Poisot2023NeutralLandscapesJulia] |
| Simulations | Stand-alone software | GradientLand | [@Cambui2015GradientLandSoftware] |
| Simulations | Stand-alone software | HexSim | [@Schumaker2018HexSimModeling] |
| Genetics | R | graph4lg | [@Savary2021Graph4lgPackage] |
| Genetics | R | landgenreport | [@Gruber2015LandgenreportNew] |
| Genetics | R | adegenet | [@Jombart2008AdegenetPackage] |
| Genetics | R | ape | [@Paradis2019Ape50] |
| Genetics | Python | Python based scripts | [@Etherington2011PythonBased] |
| Genetics | Python | SDMtoolbox 2.0 | [@Brown2017SDMtoolbox20] |
| Planning | R | prioritizr | [@Hanson2024PrioritizrSystematic] |
| Planning | R | coco | [@vanMantgem2023CocoConservation] |
| Planning | R | restoptr | [@Justeau-Allaire2023RestoptrPackage] |
| Planning | Python | CAPTAIN | [@Silvestro2022ImprovingBiodiversity] |

: Software implementing methodological developments in landscace ecology.

>>>>

<!-- MH: Double check programming languages -->

| Topic | Programming language | Software | Reference |
|:---:|:---:|:---:|:---:|
| Spatial patterns | R | sf | [@Pebesma2018SimpleFeatures] |
| Spatial patterns | R | terra | [@Hijmans2024TerraSpatial] |
| Spatial patterns | R | landscapemetrics | [@Hesselbarth2019LandscapemetricsOpensource] |
| Spatial patterns | R | multilandr | [@Huais2024MultilandrPackage] |
| Spatial patterns | R | bespatial | [@Nowosad2024BespatialBoltzmann] |
| Spatial patterns | R | rasterdiv | [@Rocchini2021RasterdivInformation] |
| Spatial patterns | R | LandComp | [@Konrad2023AdaptingMultiscale] |
| Spatial patterns | R | geodiv | [@Smith2021GeodivPackage] |
| Spatial patterns | R | glcm | [@Zvoleff2020GlcmCalculate] |
| Spatial patterns | R | vectormetrics | [@Matuszek2024VectormetricsLandscape] |
| Spatial patterns | R | motif | [@Nowosad2021MotifOpensource] |
| Spatial patterns | Python | GeoPandas | [@Jordahl2020GeopandasPython] |
| Spatial patterns | Python | Rasterio | [@Gillies2013RasterioGeospatial] |
| Spatial patterns | Python | PyLandStats | [@Bosch2019PyLandStatsOpensource] |
| Spatial patterns | Julia | GeoStats | [@Hoffimann2018GeoStatsjlHighperformance] |
| Spatial patterns | Julia | GeoInterface | [@JuliaGeoandcontributors2024GeoInterfaceJulia] |
| Spatial patterns | Stand-alone software | FRAGSTATS | [@McGarigal2023FRAGSTATSV4] |
| Spatial patterns | Stand-alone software | GuidosToolbox | [@Vogt2017GuidosToolboxUniversal] |
| Connectivity | R | ResistanceGA | [@Peterman2018ResistanceGAPackage] |
| Connectivity | R | lconnect | [@Mestre2023LconnectPackage] |
| Connectivity | R | grainscape | [@Chubaty2020ToolboxGrainscape] |
| Connectivity | Julia | Circuitscape | [@Anantharaman2019CircuitscapeJulia] |
| Connectivity | Julia | ConScape | [@vanMoorter2023AcceleratingAdvances] |
| Connectivity | Julia | Omniscape | [@Landau2021OmniscapejlSoftware] |
| Connectivity | Stand-alone software | Graphab | [@Foltete2012SoftwareTool] |
| Connectivity | Stand-alone software | Conefor | [@Saura2009ConeforSensinode] |
| Connectivity | Stand-alone software | LSCorridors | [@Ribeiro2017LandScapeCorridors] |
| Sampling | Python | ZonalMetrics | [@Adamczyk2017ZonalMetricsPython] |
| Simulations | R | NLMR | [@Sciaini2018NLMRLandscapetools] |
| Simulations | R | rflsgen | [@Justeau-Allaire2022FragmentedLandscape] |
| Simulations | Python | NLMpy | [@Etherington2015NLMpyPython] |
| Simulations | Python | Pathwalker | [@UnnithanKumar2022PathwalkerNew] |
| Simulations | Julia | NeutralLandscapes | [@Poisot2023NeutralLandscapesJulia] |
| Simulations | NetLogo | EFForTS-LGraf | [@Salecker2019EFForTSLGrafLandscape] |
| Simulations | Stand-alone software | GradientLand | [@Cambui2015GradientLandSoftware] |
| Simulations | Stand-alone software | Landscape Generator | [@vanStrien2016ImprovedNeutral] |
| Simulations | Stand-alone software | HexSim | [@Schumaker2018HexSimModeling] |
| Simulations | Stand-alone software | RangeShifter2.0 | [@Bocedi2021RangeShifter20] |
| Genetics | R | graph4lg | [@Savary2021Graph4lgPackage] |
| Genetics | R | landgenreport | [@Gruber2015LandgenreportNew] |
| Genetics | R | adegenet | [@Jombart2008AdegenetPackage] |
| Genetics | R | ape | [@Paradis2019Ape50] |
| Genetics | Python | Python based scripts | [@Etherington2011PythonBased] |
| Genetics | Python | SDMtoolbox 2.0 | [@Brown2017SDMtoolbox20] |
| Planning | R | prioritizr | [@Hanson2024PrioritizrSystematic] |
| Planning | R | CoCo | [@vanMantgem2023CocoConservation] |
| Planning | R | restoptr | [@Justeau-Allaire2023RestoptrPackage] |
| Planning | Python | CAPTAIN | [@Silvestro2022ImprovingBiodiversity] |

: Software and models that implement recent methodological advances in landscace ecology.
